---
title: "WriteUp Linear Model with prediction"   
author: "Ashley Saunders"         
date: "10/22/2024"      
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(knitr)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

## Model 1 SIMS~ARM
### Scarttered Plot
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))

```
```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```

Some of the dots in this scatter plot are exhibiting a diagonal upward trend, which indicates a positive association. This statistic demonstrates the workers' expected arm strength from the simulation. This indicates that the majority of the population should have arm strength between 50 and 100. 

### Numerical Results

```{r}
cor(SIMS~GRIP,data=data)
```

There is a clear positive correlation. Since it is getting close to 1 and increasing, we can see there is correlation between the two. 

### Inferential Results Model 1

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The line moves from the lower left corner to the upper right corner because of the positive coefficient. The numerical results make this clear with an equation SIMS=0.045463GRIP - 4.809675. 

### Create target

```{r}
target<-data.frame(ARM=88, GRIP=44)
```

### Predict Target Point of Model 1

```{r}
predict(model.1,target,interval=c("prediction"))
```

The plot predicts 0.7063836. The values are predicted to be between -1.726209 and 3.128977.



