---
title: "WriteUp Linear Model with prediction"   
author: "Ashley Saunders"         
date: "10/22/2024"      
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(knitr)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

## Model 1 SIMS~ARM
### Scarttered Plot
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))

```
```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```

Some of the dots in this scatter plot are exhibiting a diagonal upward trend, which indicates a positive association. This statistic demonstrates the workers' expected arm strength from the simulation. This indicates that the majority of the population should have arm strength between 50 and 100. 

### Numerical Results

```{r}
cor(SIMS~GRIP,data=data)
```

There is a clear positive correlation. Since it is getting close to 1 and increasing, we can see there is correlation between the two. 

### Inferential Results Model 1

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The line moves from the lower left corner to the upper right corner because of the positive coefficient. The numerical results make this clear with an equation SIMS=0.045463GRIP - 4.809675. 

### Create target

```{r}
target<-data.frame(ARM=88, GRIP=44)
```

### Predict Target Point of Model 1

```{r}
predict(model.1,target,interval=c("prediction"))
```

The plot predicts 0.7063836. The values are predicted to be between -1.726209 and 3.128977.

### Linear Fit Model 1

```{r}
basicNN + geom_point() + ggtitle("SIMS~ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method=lm)

```

## Model 2 SIMS~GRIP

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))

```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```

This shows correlation between SIMS~GRIP as the slope is positive.

### Numerical Results
```{r}
cor(SIMS~GRIP,data=data)
```
This shows high correlation because it is close to one.

### Inferential Results

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

We can predict the equation for Model 2 to be SMS=0.045463GRIP-4.809675.

### Predict Target Point of Model 2

```{r}
predict(model.1,target,interval=c("prediction"))
```
```{r}
predict(model.2,target,interval=c("prediction"))
```

Model 2 is predicted to be fit at -2.80904. It will be between -5.444714 and -0.1738933.

### Linear Fit Model 2
```{r}
basicNN + geom_point() + ggtitle("SIMS~GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method=lm)
```

## Model 3 SIMS~ARM+GRIP

### Numerical Results
```{r}
cor(SIMS~ARM,data=data)
```
```{r}
cor(SIMS~GRIP,data=data)
```
```{r}
cor(SIMS~ARM+GRIP,data=data)
```

Model 3 has very high positive correlation compared to the other 2. 

### Inferential Results

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

The equation is SIMS=0.037311ARM + 0.024470GRIP + 5.433871. This is the predicted 3D line.

### Predict Target Point for Model 3
```{r}
predict(model.1,target,interval=c("prediction"))

```
```{r}
predict(model.2,target,interval=c("prediction"))

```
```{r}
predict(model.3,target,interval=c("prediction"))

```

The model shows -1.073855 predicted. The value is between -3.462155 and 1.314444.

### Anova Tests for Models

### Model 1~Model 3
```{r}
anova(model.1,model.3)
```

The p-value is shown to be very small. Model 3 is better than model 1 because the test shows Model 1 had 217.88 errors and Model 3 had 188.43 errors.

### Model 2~Model 3
```{r}
anova(model.2,model.3)
```

The p-value is predicted to be 0.000000001495. Model 3 has less errors than model 2. Model 3 would be most accurate.

### Model 1~Model 2
```{r}
anova(model.1,model.2)
```

Model 1 has less errors than model 2, making model 1 better than model 2 shown by the data.



